Visualization

### 2023-01-08 Code/simulation.Rmd
New Data

```{r ma = .3, n = 8000}
n <- 8000
blksize <- 20
theta <- .3
target <- c(0, 1, theta / (1 + theta^2))
set.seed(4567)
sim_.3_8k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
mychk(sim_.3_8k, target)
```

>>>>

```{r ma = .3, n = 8000}
n <- 8000
blksize <- 20
theta <- .3
target <- c(0, 1, theta / (1 + theta^2))
set.seed(4567)
sim_.3_8k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
mychk(sim_.3_8k, target)
```
```{r}
write.csv(sim_.3_125,"../Data/Raw/sim_.3_125.csv", row.names = FALSE)
write.csv(sim_.3_1k,"../Data/Raw/sim_.3_1k.csv", row.names = FALSE)
write.csv(sim_.3_3375,"../Data/Raw/sim_.3_3375.csv", row.names = FALSE)
write.csv(sim_.3_8k,"../Data/Raw/sim_.3_8k.csv", row.names = FALSE)
```
